---
title: "Departmental Attrition Rates"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    navbar:
      - { title: "Dashboard Creator",
          href: 'https://www.linkedin.com/in/hughwelchdata',
          align: right }
editor_options: 
  chunk_output_type: console
---


<!-- 

Author: Hugh Welch
Linked In: https://www.linkedin.com/in/hughwelchdata


Built with
------------------------------------------------------------
R Version: 4.1.2
RStudio Version: 1.4.1106
------------------------------------------------------------


Notes:
------------------------------------------------------------
This example is intended to demonstrate some of the ways you can use readily
available packages in R to develop static files containing client-side
interactivity including tooltips, highlighting, and filtering.
This is a handy way to create .html files that can be sent via email or
uploaded to a shared repository for access by multiple users concurrently.
You can also convert the files to .apsx for upload to SharePoint as well.
This technique is not meant as a replacement for Shiny, but as a workaround if
Shiny is not an option. Please note that this methodology does not scale as 
efficiently as a server based approach.

Thank you so much to the awesome teams of people who work to make these 
packages available to the open source community and maintain them!!! 
I especially appreciate Carson Sievert and Joe Cheng for the amazing resources 
they make freely available.
For additional information see https://plotly-r.com/client-side-linking.html
 -->


```{css my-content, echo=FALSE}
    .value-box .caption {
    font-size: 20px; font-weight: bold;}

# increases valuebox text size

```


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(plotly)
library(flexdashboard)
library(tidymodels)
library(crosstalk)
library(scales)
library(htmlwidgets)
library(DT)

# library(skimr)
# library(DataExplorer)

# I use the skimr and dataexplorer packages when getting to grips
# with new datasets but they're not necessary to build the final output

```


```{r load_data}

data("attrition")

df <- attrition

# duplicating the dataset is not necessary but I kept introducing so many errors
# by confusing the "attrition" dataset with the "Attrition" field in the 
# "attrition" dataset that I just made a copy to mentally keep them separate
# ...in hindsight I guess I could have just renamed the field...

```


```{r valuebox_aggregates}

value_box_agg <-
  df %>%
  summarise(
    Department = 'Total',
    count = n(),
    attrition_rate = sum(Attrition == 'Yes') / count,
    jobsat_topbox = sum(JobSatisfaction == 'Very_High') / count,
    mean_mnthincom = dollar(
      mean(MonthlyIncome),
      accuracy = 1.0,
      big.mark = ','
    )
  ) %>%
  ungroup() %>%
  bind_rows(
    df %>%
      group_by(Department) %>%
      summarise(
        count = n(),
        attrition_rate = sum(Attrition == 'Yes') / count,
        jobsat_topbox = sum(JobSatisfaction == 'Very_High') / count,
        mean_mnthincom = dollar(
          mean(MonthlyIncome),
          accuracy = 1.0,
          big.mark = ','
        )
      ) %>%
      ungroup()
  ) %>%
  mutate(Department = str_replace_all(Department, '_', ' ')) %>%
  mutate(count = comma(count, accuracy = 1.0)) %>%
  mutate(across(c(attrition_rate, jobsat_topbox),
                ~ percent(., accuracy = 0.1)))

# creates a dataframe of aggregate values for use in the BAN valuebox captions

```


```{r set_department_colors}

# # default colors
# department_colors <- c('Total' = '#263238',
#                        'Human Resources' = '#0D47A1',
#                        'Research Development' = '#00796B',
#                        'Sales' = '#880E4F')

# this was the first attempt for the valuebox colors that will also serve as 
# the legend for the landing page. I eventually needed them to be a little 
# lighter so you can see the caret icon indicating your current page

# I love the quick color reference built the R at the link below
# https://chichacha.netlify.app/2018/12/09/having-bit-of-party-with-material-colour-palette/




# default colors
department_colors <- c('Total' = '#455A64',
                       'Human Resources' = '#1565C0',
                       'Research Development' = '#00897B',
                       'Sales' = '#AD1457')


```


```{r set_page_links}

department_links <- c('Total' = 'total',
                       'Human Resources' = 'hr',
                       'Research Development' = 'rd',
                       'Sales' = 'sales-1')

```


```{r valuebox_function}

active_icon <- 'fa-caret-left'


vb_func <- function(department, active) {
  
  dep <- str_to_title(department)
  
  caption_values <-
    value_box_agg %>% filter(Department == department)
  
  valueBox(
    value = str_to_title(department),
    color = department_colors[dep],
    href = paste0('#', str_to_lower(department_links[dep])),
    
    icon = if_else(active, active_icon, ''),
    
    caption = paste0(
      if_else(active, '<i>', ''),
      'Employees: <b>',
      caption_values$count,
      '</b><br>',
      'Attrition Rate: <b>',
      caption_values$attrition_rate,
      '</b><br>',
      'Very High Job Satisfaction: <b>',
      caption_values$jobsat_topbox,
      '</b><br>',
      'Mean Monthly Income: <b>',
      caption_values$mean_mnthincom,
      '</b>',
      if_else(active, '</i>', '')
    )
  )
  
}

# creates function that will build the valueboxes based on department and
# active page arguments. These will serve as page navigation and as
# the color legend on the landing page

```







Total 
=======================================




Column {data-width=250}
---------------------------------------


### Total

```{r Total_valuebox_total}

vb_func('Total', TRUE)

```



### Sales

```{r Total_valuebox_sales}

vb_func('Sales', FALSE)

```



### Research Development

```{r Total_valuebox_research_development}

vb_func('Research Development', FALSE)

```



### Human Resources

```{r Total_valuebox_human_resources}

vb_func('Human Resources', FALSE)

```





Column {data-width=300}
---------------------------------------

### Attrition Rates by Job

```{r Total_Attrition_Rates_by_Job}

total_by_job_df <-
  df %>%
  mutate(across(c(Department, JobRole),
                ~ str_replace_all(., '_', ' '))) %>%
  left_join(tibble(
    Department = c('Human Resources',
                   'Research Development',
                   'Sales'),
    abbrv = c('HR',
              'R&D',
              'Sales')
  )) %>%
  mutate(job = paste0(abbrv, ' - ', JobRole)) %>%
  group_by(Department,
           JobRole,
           job) %>%
  summarise(
    count = n(),
    attrition_count = sum(Attrition == 'Yes'),
    attrition_rate = attrition_count / count
  ) %>%
  ungroup()



# vline and text copied from https://plotly.com/r/horizontal-vertical-shapes/

vline <- function(x = 0, color = department_colors['Total']) {
  list(
    type = 'line',
    y0 = 0,
    y1 = 1,
    yref = 'paper',
    x0 = x,
    x1 = x,
    opacity = 0.25,
    line = list(color = color, dash = 'dot')
  )
}


a <- function(x = 0, color = department_colors['Total']) {
  list(
    type = 'line',
    y = 0.25,
    yref = 'paper',
    x = x,
    color = color,
    text = '<i>baseline</i>',
    textposition = 'left',
    showarrow = FALSE
  )
}




baseline <- sum(df$Attrition == 'Yes') / NROW(df)






# creating custom tooltips with simple html tags helps add a ton of on-demand
# context. I can't wait for the day we figure out how to replicate
# Tableau's in-tooltip charts in a static file


total_by_job_df %>%
  
  plot_ly(
    x = ~ attrition_rate,
    y = ~ reorder(job, attrition_rate),
    color = ~ Department,
    colors = department_colors
  ) %>%
  
  add_bars(
    text = ~ paste0(
      'Department: <b>',
      Department,
      '</b><br>',
      'Job: <b>',
      JobRole,
      '</b><br>',
      'Attrition Rate: <b>',
      percent(attrition_rate,
              accuracy = 0.01),
      '</b><br>',
      'Count: <b>',
      attrition_count,
      ' of ',
      count,
      ' employees</b>'
    ),
    hoverinfo = 'text',
    textposition = 'none' # don't forget this or you might see some weird labels
  ) %>%
  
  add_text(
    text = ~ paste0(
      ' <b>',
      percent(attrition_rate,
              accuracy = 0.01),
      '</b><br>',
      '<i> ',
      attrition_count,
      ' of ',
      count,
      ' empl.</i>'
    ),
    textposition = 'right',
    hoverinfo = 'none'
  ) %>%
  
  layout(
    showlegend = FALSE,
    yaxis = list(title = FALSE,
                 ticksuffix = ' '),
    xaxis = list(
      title = list(text = 'Attrition Rate <i>(lower is better)</i>'),
      tickformat = '1%',
      range = ~ c(0,
                  max(attrition_rate * 1.5)) # helps provide space for labels
    ),
    shapes = list(vline(baseline)),
    annotations = list(a(0.06 + baseline))
  ) %>%
  config(displayModeBar = FALSE)

```





Column {data-width=450}
---------------------------------------

### Numeric Variables Comparison &nbsp;&nbsp; <i>Hover for Details</i>

```{r Total_Numeric_Variable_Comparison}

yes_no_colors <- c('Yes' = '#FF6F00',
                   'No' = '#BDBDBD')

# creating singular references for re-used colors saves a lot of headache
# and time spent searching your code for that one place you forgot to change
# from gray300 to gray400....



variable_cont_pivot_df <-
  df %>%
  select(Attrition,
         where(is.numeric)) %>%
  pivot_longer(
    cols = c(Age:YearsWithCurrManager),
    names_to = 'measure',
    values_to = 'values'
  ) %>%
  group_by(measure) %>%
  mutate(zscore = scale(values)[, 1]) %>%
  ungroup()


variable_cont_levels <-
  variable_cont_pivot_df %>%
  group_by(measure, Attrition) %>%
  summarise(median_z = median(zscore),
            median_value = median(values)) %>%
  ungroup() %>%
  pivot_wider(names_from = Attrition,
              values_from = c(median_z, median_value)) %>%
  mutate(z_diff = abs(median_z_Yes - median_z_No)) %>%
  arrange(desc(z_diff)) %>%
  mutate(across(c(median_z_Yes, median_z_No),
                ~ round(., 3)))





cont_var_chart <-
  variable_cont_levels %>%
  plot_ly(x = ~ reorder(measure, (z_diff))) %>%
  add_segments(
    xend = ~ reorder(measure, (z_diff)),
    y = ~ median_z_No,
    yend = ~ median_z_Yes,
    color = I('#000000'),
    name = 'Variable Impact on Attrition',
    hoverinfo = 'none'
  ) %>%
  add_markers(
    y = ~ median_z_Yes,
    color = I(yes_no_colors['Yes']),
    size = I(80),
    name = 'Attrition - Yes',
    text = ~ paste0(
      'Attrition: <b>Yes</b><br>',
      'Variable: <b>',
      measure,
      '</b><br>',
      'Median Z Score: <b>',
      median_z_Yes,
      '</b><br>',
      'Median Value: <b>',
      median_value_Yes,
      '</b>'
    ),
    hoverinfo = 'text'
  ) %>%
  add_markers(
    y = ~ median_z_No,
    color = I(yes_no_colors['No']),
    size = I(80),
    name = 'Attrition - No',
    text = ~ paste0(
      'Attrition: <b>No</b><br>',
      'Variable: <b>',
      measure,
      '</b><br>',
      'Median Z Score: <b>',
      median_z_No,
      '</b><br>',
      'Median Value: <b>',
      median_value_No,
      '</b>'
    ),
    hoverinfo = 'text'
  ) %>%
  layout(
    legend = list(
      orientation = 'h',
      x = 0.01,
      y = 0.99,
      xanchor = 'left'
    ),
    xaxis = list(title = FALSE),
    yaxis = list(title = 'Difference in Median Z Score'),
    title = FALSE,
    hovermode = 'x'
  ) %>%
  config(displayModeBar = FALSE)




cont_var_chart

```



### Categorical Variables Comparison &nbsp;&nbsp; <i>Hover for Details</i>

```{r Total_Categorical_Variables}

variable_discr_pivot_df <-
  df %>%
  select(-c(JobRole, Department)) %>%
  select(Attrition, !where(is.numeric)) %>%
  mutate_all(as.character) %>%
  pivot_longer(
    cols = c(BusinessTravel:WorkLifeBalance),
    names_to = 'measure',
    values_to = 'values'
  ) %>%
  count(Attrition,
        measure,
        values) %>%
  ungroup() %>%
  pivot_wider(names_from = Attrition,
              values_from = n) %>%
  mutate(perc_yes = Yes / (Yes + No)) %>%
  arrange(measure,
          values,
          perc_yes) %>%
  group_by(measure) %>%
  mutate(clr = as.character(row_number())) %>%
  ungroup() %>%
  mutate(
    above_mean = case_when(
      perc_yes > mean(perc_yes) + sd(perc_yes)
      ~ 'High % Yes',
      perc_yes <= mean(perc_yes) + sd(perc_yes) &
        perc_yes >= mean(perc_yes) - sd(perc_yes)
      ~ 'Medium % Yes',
      perc_yes < mean(perc_yes) - sd(perc_yes)
      ~ 'Low % Yes',
      TRUE ~ 'err'
    )
  )





discr_var_chart <-
  variable_discr_pivot_df %>%
  plot_ly(x = ~ reorder(measure,
                        FUN = max,
                        X = perc_yes),
          y = ~ perc_yes) %>%
  add_bars(
    color = ~ above_mean,
    colors = c(
      'High % Yes' = '#E57373',
      'Medium % Yes' = '#AB47BC',
      'Low % Yes' = '#29B6F6',
      'err' = '#CFD8DC'
    ),
    text = ~ paste0(
      'Variable: <b>',
      measure,
      ' - ',
      values,
      '</b><br>',
      'Percent Attrition Yes: <b>',
      percent(perc_yes,
              accuracy = 0.01),
      '</b><br>',
      'Range: <b>',
      above_mean,
      '</b>'
      
    ),
    hoverinfo = 'text',
    name = ~ values,
    legendgroup = ~ above_mean,
    showlegend = FALSE,
    textposition = 'none',
    marker = list(line = list(color = '#FFFFFF',
                              width = 1))
  ) %>%
  layout(
    barmode = 'relative',
    hovermode = 'x',
    title = FALSE,
    yaxis = list(
      tickformat = '1%',
      title = list(text = 'Percent Attrition - Yes'),
      showticklabels = FALSE
    ),
    xaxis = list(title = FALSE)
  ) %>%
  config(displayModeBar = FALSE)



discr_var_chart

```







Sales
=======================================




Column {data-width=250}
---------------------------------------


### Total

```{r Sales_valuebox_total}

vb_func('Total', FALSE)

```



### Sales

```{r Sales_valuebox_sales}

vb_func('Sales', TRUE)

```



### Research Development

```{r Sales_valuebox_research_development}

vb_func('Research Development', FALSE)

```



### Human Resources

```{r Sales_valuebox_human_resources}

vb_func('Human Resources', FALSE)

```


<!-- 
keeping the same BAN valueboxes for each page if possible allows you to use
them for page navigation and I think it makes the final product
feel more cohesive
-->




Column{data-width=275}
--------------------------------------




```{r Sales_Shared_Data}


sales_jobrole_categorical_sd <-
  df %>%
  filter(Department == 'Sales') %>%
  select(-Department) %>% 
  select(Attrition,
         JobRole,!where(is.numeric)) %>%
  mutate_all(as.character) %>%
  pivot_longer(
    cols = c(BusinessTravel:WorkLifeBalance),
    names_to = 'variable',
    values_to = 'value'
  ) %>%
  group_by(JobRole,
           variable,
           value) %>%
  summarise(attrition_yes = sum(Attrition == 'Yes'),
            count = n()) %>%
  ungroup() %>%
  group_by(JobRole,
           variable) %>% 
  mutate(attrition_rate = attrition_yes / sum(count)) %>% 
  arrange(JobRole,
          variable,
          desc(attrition_rate)) %>% 
  mutate(y_axis_index = row_number()) %>% 
  ungroup() %>% 
  group_by(variable) %>% 
  mutate(x_axis_index = max(attrition_rate)) %>% 
  ungroup() %>%  
  SharedData$new(key = ~ JobRole,
                 group = 'SD_SalesJobRole')



```







### Sales Job Roles


```{r Sales_Job_Roles}

sales_jobrole_categorical_sd %>% 
  plot_ly() %>% 
  group_by(JobRole) %>% 
  summarise(attrition_rate = sum(attrition_yes) / sum(count)) %>% 
  add_bars(x = ~ reorder(JobRole,
                         desc(attrition_rate)),
           y = ~ attrition_rate,
           color = I(department_colors['Sales']),
           text = ~ paste0('Job Role:<b>',
                           JobRole,
                           '</b><br>',
                           'Attrition Rate: <b>',
                           percent(attrition_rate,
                                   accuracy = 0.1),
                           '</b>'),
           hoverinfo = 'text',
           textposition = 'none') %>% 
  add_text(x = ~ reorder(JobRole,
                         desc(attrition_rate)),
           y = ~ attrition_rate,
           color = I(department_colors['Sales']),
           text = ~ percent(attrition_rate,
                            accuracy = 0.1),
           textposition = 'top',
           hoverinfo = 'none') %>% 
  layout(yaxis = list(title = 'Attrition Rate',
         tickformat = '0.1%',
         range = ~ c(0, max(attrition_rate) * 1.15)),
         xaxis = list(title = FALSE),
         showlegend = FALSE,
         barmode = 'overlay'
         ) %>%
  highlight() %>% 
  config(displayModeBar = FALSE)


```





### Filter


```{r Sales_Filter}


filter_select(
  id = 'SD_SalesJobRole',
  label = 'Select Role',
  sharedData = sales_jobrole_categorical_sd,
  group = ~ JobRole,
  multiple = FALSE
)


```







Column{data-width=475}
--------------------------------------


### Sales Response Distributions

```{r Sales_Response_Distributions}


sales_jobrole_categorical_sd %>% 
  plot_ly() %>% 
  add_heatmap(x = ~ reorder(variable,
                            desc(x_axis_index)),
              y = ~ y_axis_index,
              z = ~ attrition_rate,
              text = ~ paste0('Category: <b>',
                              variable,
                              '</b><br>',
                              'Value: <b>',
                              value,
                              '</b><br>',
                              'Attrition Rate: <b>',
                              percent(attrition_rate,
                                      accuracy = 0.1),
                              '</b>'),
              hoverinfo = 'text',
              xgap = 1,
              ygap = 1) %>% 
  colorbar(title = list(text = 'Attrition Rate'),
           tickformat = '0.1%') %>% 
  layout(title = list(text = '<b>Attrition Rates by Category</b>',
                      x = 0.05),
         margin = list(t = 50),
         xaxis = list(title = FALSE,
                      showgrid = FALSE),
         yaxis = list(title = '<i><b>hover over grid for data</b></i>',
                      showticklabels = FALSE,
                      ticks = '',
                      showgrid = FALSE))




```







RD
=======================================



Column {data-width=250}
---------------------------------------


### Total

```{r RD_valuebox_total}

vb_func('Total', FALSE)

```



### Sales

```{r RD_valuebox_sales}

vb_func('Sales', FALSE)

```



### Research Development

```{r RD_valuebox_research_development}

vb_func('Research Development', TRUE)

```



### Human Resources

```{r RD_valuebox_human_resources}

vb_func('Human Resources', FALSE)

```








```{r RD_Shared_Data}

rd_sd <-
  df %>%
  filter(Department == 'Research_Development') %>%
  SharedData$new(key = ~ Attrition,
                 group = 'SD_RD_Attrition')


```








Column {data-width=750}
---------------------------------------



### Research and Development Scatterplot with Marginal Distribution  &nbsp;&nbsp; <i>Hover Over Point for Details</i>


```{r RD_Scatterplot}

subplot(
  nrows = 2,
  widths = c(0.8, 0.2),
  heights = c(0.2, 0.8),
  shareX = TRUE,
  shareY = TRUE,
  
  rd_sd %>%
    plot_ly(x = ~ MonthlyIncome) %>%
    add_boxplot(
      color = ~ Attrition,
      colors = yes_no_colors,
      showlegend = TRUE
    ),
  
  plotly_empty(),
  
  rd_sd %>%
    plot_ly(x = ~ MonthlyIncome,
            y = ~ Age) %>%
    add_markers(
      color = ~ Attrition,
      colors = yes_no_colors,
      text = ~ paste0(
        'Attrition: <b>',
        Attrition,
        '</b><br>',
        'Monthly Income: <b>',
        MonthlyIncome,
        '</b><br>',
        'Age: <b>',
        Age,
        '</b><br>',
        'Business Travel: <b>',
        BusinessTravel,
        '</b><br>',
        'Education: <b>',
        Education,
        '</b><br>',
        'Education Field: <b>',
        EducationField,
        '</b><br>',
        'Environmental Satisfaction: <b>',
        EnvironmentSatisfaction,
        '</b><br>',
        'Gender: <b>',
        Gender,
        '</b><br>',
        'Job Involvement: <b>',
        JobInvolvement,
        '</b><br>',
        'Job Role: <b>',
        JobRole,
        '</b><br>',
        'Job Satisfaction: <b>',
        JobSatisfaction,
        '</b><br>',
        'Marital Status: <b>',
        MaritalStatus,
        '</b><br>',
        'Overtime: <b>',
        OverTime,
        '</b><br>',
        'Performance Rating: <b>',
        PerformanceRating,
        '</b><br>',
        'Relationship Satisfaction: <b>',
        RelationshipSatisfaction,
        '</b><br>',
        'Work-Life Balance: <b>',
        WorkLifeBalance,
        '</b>'
      ),
      hoverinfo = 'text',
      textposition = 'none',
      alpha = 0.65,
      size = 1,
      showlegend = FALSE
    ) %>%
    layout(
      xaxis = list(
        tickformat = '$1',
        title = 'Monthly Income',
        showspikes = TRUE,
        spikecolor = '#212121',
        spikethickness = 1,
        spikemode = 'toaxis+across'
      ),
      yaxis = list(
        showspikes = TRUE,
        spikecolor = '#212121',
        spikethickness = 1,
        spikemode = 'toaxis+across'
      )
    ) %>%
    toWebGL(),
  
  
  rd_sd %>%
    plot_ly(y = ~ Age) %>%
    add_boxplot(
      color = ~ Attrition,
      colors = yes_no_colors,
      showlegend = FALSE
    )
) %>%
  
  highlight(on = 'plotly_hover',
            selected = attrs_selected(showlegend = FALSE)) %>%
  
  config(displayModeBar = FALSE)


# I really like the additional context marginal distributions can add to 
# a scatterplot. Combined with cross-axis spike lines you can easily 
# see exactly where each point lies

```





HR
=======================================



Column {data-width=250}
---------------------------------------


### Total

```{r HR_valuebox_total}

vb_func('Total', FALSE)

```



### Sales

```{r HR_valuebox_sales}

vb_func('Sales', FALSE)

```



### Research Development

```{r HR_valuebox_research_development}

vb_func('Research Development', FALSE)

```



### Human Resources

```{r HR_valuebox_human_resources}

vb_func('Human Resources', TRUE)

```











```{r HR_Shared_Data}

hr_sd <-
  df %>%
  filter(Department == 'Human_Resources') %>%
  arrange(TotalWorkingYears) %>%
  mutate(rn = as.character(row_number()),
# I spent about an hour troubleshooting this piece before realizing that
# the "rn" key I created was numeric and being treated as such for the 
# slider filter. I wish I could say this was the first time I've forgotten
# this key detail...

         cnt = 1) %>%
  select(rn,
         Attrition,
         Department,
         TotalWorkingYears,
         everything()) %>%
  
  SharedData$new(key = ~ rn,
                 group = 'HR_SD')

```






Column {data-width=250}
---------------------------------------



### Total Working Years Slider


```{r HR_Slider}

filter_slider(id = 'hr_slider',
              label = 'Total Working Years',
              sharedData = hr_sd,
              column = ~ TotalWorkingYears)

```





### Attrition Donut

```{r HR_Donut}

  hr_sd %>%
    plot_ly() %>%
    group_by(Attrition) %>%
    summarise(n = n()) %>%
    add_pie(labels = ~ Attrition,
            values = ~ n,
            hole = 0.55,
            hoverinfo = 'none',
            marker = list(line = list(width = 2,
                               color = '#FFFFFF'))) %>% 
  layout(
    title = list(text = 'Human Resources Attrition',
                 x = 0.05),
    margin = list(t = 50),
    legend = list(
      x = 0.5,
      y = 0.5,
      xanchor = 'center',
      yanchor = 'center'
    )
  ) %>%
  highlight(on = 'plotly_selected') %>%
  config(displayModeBar = FALSE)


# people seem to hate pie charts but often lack such animosity towards
# donut charts. Not sure why, but I personally like the fact that I can put the 
# legend inside the donut when screen space is at a premium

```







Column {data-width=500}
---------------------------------------






### Human Resources Data Table

```{r HR_Data_Table}

hr_sd %>% 
  datatable(
    extensions = 'Buttons',
    options = list(
      pageLength = 10000,
      fillContainer = TRUE,
      scrollY = 690,
# something changed a while back in the DT package and now you have to specify
# a Y scroll or your tables get chopped off
      scrollCollapse = TRUE,
      scrollX = TRUE,
      columnDefs = list(
        list(className = 'dt-center', targets = '_all'),
        list(visible = FALSE, targets = c(0))),
      
      dom = 'Bfrt',
      buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
# export options help with the "your dashboard is great, but can I 
# get it in excel?" request that always seems inevitable
    ),
    rownames = FALSE
  )

```






<!--


Final Notes
------------------------------------------------------------

I hope you found this brief demonstration helpful. I've tried to create
something I would have liked to have had when I first started using plotly
and client-side interactivity. 

I won't claim to be an expert as I've picked up most of my R knowledge from
google, youtube, stackoverflow, reading the O'Reilly books with the animals
on the covers, and from making more mistakes than I care to think about.

This approach evolved from having to work around the constraints of not 
being able to have or use a Shiny server and develop fully functional apps
due to the nature of data I work with. That being said, this has been my
go-to way of developing and sharing reports and analyses internally and
works well within the scope of my limited audience.
I would be hesitant to try and scale this approach beyond a relatively
tightly controlled process or to use as a direct replacement for Shiny. 

If you have any questions or want to reach out, please feel free to shoot me a
message at my Linked In page https://www.linkedin.com/in/hughwelchdata
I'm usually more responsive there than email or github.

 - Hugh

-->


















